\documentclass[11pt]{article}

\usepackage{a4wide}
\usepackage{mathptm}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{shapes.misc, positioning}
\usepackage{listings}
\usepackage{color}
\usepackage{xcolor}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=left,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
\begin{document}

\title{Report SpringApp Project Group 4}

\author{Jacek Antoni Wegrzynowski, Rashaad Wells Iversen, Veronicha C. T. Pettersen }

\maketitle

\begin{abstract}

\textcolor{red}{ 10-15 lines with the software technology and the highlights from the project that has been undertaken. }

This document describes the journey of a group of students at Western Norway University of Applied Sciences took to develop a web-based application prototype to create poll and receive votes.  The prototype's creation involved a new learned technology stack, integrating Angular, Spring Boot, JPA, Hibernate, H2, MQTT and Java.  We achieved significant functionalities, including user registration and authentication, poll and question creation, poll searching, and versatile voting mechanisms via both web interface and IoT integration.  Remarkably, these milestones were reached despite the team's initial lack of Java expertise, demonstrating a commendable learning curve and adaptability.  The successful implementation of these features showcases the prototype's potential to deliver a final product for polling.  While the complexity of our work may not align with every expectation, we take considerable pride in the achievements we have realized.  Our efforts reflect significant dedication and learning, particularly in areas initially unfamiliar to us.

\end{abstract}

%\input{commands}

\input{sections/introduction}

\input{sections/technology}

\input{sections/design}

\input{sections/implementation}

\input{sections/evaluation}

\input{sections/conclusion}

\bibliographystyle{plain}
\bibliography{report.bib}{}

\end{document}
